% Created 2014-09-17 Wed 15:40
\documentclass[10pt,b5paper]{article}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{xeCJK}
\usepackage{longtable}
\usepackage{float}
\usepackage{textcomp}
\usepackage{geometry}
\geometry{left=0cm,right=0cm,top=0cm,bottom=0cm}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{latexsym}
\usepackage{natbib}
\usepackage{fancyhdr}
\usepackage[xetex,colorlinks=true,CJKbookmarks=true,linkcolor=blue,urlcolor=blue,menucolor=blue]{hyperref}


\usepackage{CJKutf8}
\begin{CJK}{UTF8}{gbsn}
\lstset{language=c++,numbers=left,numberstyle=\tiny,basicstyle=\ttfamily\small,tabsize=4,frame=none,escapeinside=``,extendedchars=false,keywordstyle=\color{blue!70},commentstyle=\color{red!55!green!55!blue!55!},rulesepcolor=\color{red!20!green!20!blue!20!}}
\author{Emeth Thompson, Heyan Huang, Matthew Brown, Paul Bailey, Ranger Adams}
\date{\today}
\title{Team Contract}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.3.1 (Org mode 8.2.7c)}}
\begin{document}

\maketitle
\tableofcontents


\section{Team Name and Mission}
%\label{sec-1}
\subsection{What is your team name?}
\label{sec-1-1}
Tower Illuminati

Github Repository: \url{https://github.com/PaulCode/Tower-iLLuminati/}

\subsection{What is the mission of your team in 1-2 sentences?}
\label{sec-1-2}
Design a new and improved tower animator software. Improvements are defined as user interface changes, new features, and internal alterations which result in easier light show production. 

\section{Membership}
\label{sec-2}
\subsection{Who are the team members?}
\label{sec-2-1}
\begin{center}
\begin{tabular}{llll}
\hline
Name & Vandal Mail & Gmail Account & Github Account\\
\hline
Adams, Ranger & adam6860@vandals.uidaho.edu & pyro1370@gmail.com & Rangera\\
Bailey, Paul & bail1806@vandals.uidaho.edu & yopaulbailey@gmail.com & PaulCode\\
Brown, Matthew & matt2714@vandals.uidaho.edu & matthewbrown92@gmail.com & 1BADragon\\
Huang, Heyan & heyanh@vandals.uidaho.edu & heyan.huang2010@gmail.com & deepwaterooo\\
Thompson, Emeth & thom5468@vandals.uidaho.edu & princesstastelikechicken@gmail.com & thom5468\\
\hline
\end{tabular}
\end{center}

\subsection{What consultants/mentors/instructional staff are associated with this team?}
\label{sec-2-2}
Burce Bolden, course instructor and project mentor.

\section{Roles and Responsibilities}
\label{sec-3}
 

\subsection{Who will be the primary client Contract?}
\label{sec-3-1}
Robert Rinker is primary client contact. Our client is the University of Idaho ACM chapter since they are the hosts of the Tower Lights show.  

\subsection{Who will organize team meetings?}
\label{sec-3-2}
Emeth Thompson will organize team meetings, and Paul Bailey will be the backup. 

\subsection{Who will be in charge of keeping team documentation?}
\label{sec-3-3}
Matthew Brown will document meeting minutes, and Heyan Huang will be the backup. 

\subsection{What other roles are critical to team success?}
\label{sec-3-4}
\begin{center}
\begin{tabular}{|l|l|l|}
		\hline
		Role & Assigned Member & Secondary Member\\
		\hline
		Repository Manger & Paul Bailey & Ranger Adams \\
		Lead Programmer & Ranger Adams & Heyan Huang \\
		Project Documentation & All Team Members & \\
		Project Portfolio & Matt Brown & Emeth Thompson \\
		Project Manager & Emeth Thompson & \\
		\hline
\end{tabular}
\end{center}

- Repository Manger: Will ensure that the project repository is maintained. Maintenance includes but is not limited to performing back-ups, tracking working versions, rolling back to working versions, identifying and resolving merge conflicts, etc...
\\
\\
- Lead Programmer: The lead programmer will take on varying responsibilities as the project progresses but all will focus around the projects source code. Initially they should take a critical approach to answering the question, "How will the project design choices translate to code?" Then be our main code reviewer to ensure that the project design is accurately represented and that code falls within professional standards for style and quality.
\\
\\
- Project Documentation: All team members are expected to participate in the design and documentation process. Documentation includes Software Specifications, Design Specifications, class diagram, ER diagram, GUI designs, and other documents which help represent project design choices.
\\                
\\
- Project Portfolio: This role is specific to who physically manages the portfolio; i.e., who takes the portfolio with them, prints relevant documents, and places them in the portfolio. This role does not require that the contents of portfolio documents are that members responsibility.
\\                
\\
- Project Manager: This role is responsible for tracking the project's progress from a "big-picture" perspective. They will communicate to all team members schedules, todos, expectations, responsibilities, and all other relevant information. This role will organize all other coordination requirements to enable team member collaboration and allow roles to function at optimal performance.

\subsection{How will roles be selected/assigned?}
\label{sec-3-5}
All team member's individual roles and responsibilities are decided as a group. 


\section{Team Relationships}
\label{sec-4}
Relationships among team members must support professional and respectful engagement of all members for the benefit of the entire team. 

\section{Joint Work}
\label{sec-5}

\subsection{Purposes of Joint Work}
\label{sec-5-1}
Team members will work together to establish collective goals, design decisions and work productively to advance teamwork and project success. Some tasks will be assigned to multiple members in which case those members will organize themselves to complete the task. 

\subsection{Team Meetings}
\label{sec-5-2}

\subsection{Where and when will the team meet?}
\label{sec-5-3}
Locations: Matt's Student Office on Basement floor right near the elevator or the CSAC.

Time: Every Tuesday and Thursday at 2:30pm. We are designated to meet with our mentor every other Thursday at 3:30.

\subsection{What components are required in team meeting agendas?}
\label{sec-5-4}
Team meetings will be a discussion time for all subjects relevant to the project. Each meeting will review state of the project, the upcoming schedule, immediate tasks to accomplish and issues to overcome. 

\subsection{How will meeting minutes be taken/circulated?}
\label{sec-5-5}
Meetings will be recorded in a written bullet-point style format and then uploaded to the project drive. We have established that all members have access to the google drive for our project.  

\section{Individual Work}
\label{sec-6}

\subsection{How will work assignments be made?}
\label{sec-6-1}
Tasks will be assigned during team meetings. Assignments specific to a team member's role will likely be assigned to that team member. All tasks will be assigned through team discussion and agreement of all team members is required for a task to be assigned.

\subsection{How will quality expectations be established and verified?}
\label{sec-6-2}
All team member's work is subject to critique by the rest of the team. Each assigned task will defined by the entire team during meetings. Team members who are unsatisfied with another member's work is responsible for communicating their concern through email or team meetings. Response to concerns will be handled on a individual basis.  

\subsection{How will due dates be established and verified?}
\label{sec-6-3}
Team members that have been assigned a task are expected to complete that task by a given deadline. Deadlines will be proposed by the project manager and then discussed with the team. All members must agree upon an assignment deadline. A member has completed their task if their work matches the definition of the assigned task. A member has met their deadline if it has been completed by the date of the given deadline.


\section{Documentation and Communication}
\label{sec-7}

\subsection{What Individual documentation will be kept?}
\label{sec-7-1}
Each of our team members has a personal engineering notebook where they will keep their own notes about the project.  

\subsection{What team documentation will be kept?}
\label{sec-7-2}
Our team will document meeting minutes and the entirety of our project will be documented in our project portfolio.

\subsection{What are acceptable forms of communication?}
\label{sec-7-3}
All client communication should be written. If we have a client meeting then a written transcript should be created so that all members have access to its content. 

Team communication includes emails, text messages, phone calls, and in person verbal communication.

\section{Conflict Resolution}
\label{sec-8}
The team will strive to resolve conflicts quickly and to the satisfaction and benefit of everyone involved. 

\subsection{What process will be used to address Conflicts?}
\label{sec-8-1}
Members should attempt to resolve conflicts between themselves and if necessary the team will become involved.

\subsection{How will team dynamics be communicated to instructors/mentors?}
\label{sec-8-2}
The project manager will write a semi-weekly progress report to our instructor. In this progress report will highlight issues regarding team dynamics.

\section{Amendments}
\label{sec-9}
\subsection{Where will this team contract be kept?}
\label{sec-9-1}
The printed and signed team contract will be placed in the project portfolio and a digital version will be saved on the teams shared google drive.

\subsection{How often will the Contract be reviewed?}
\label{sec-9-2}
The team contract will be reviewed at the beginning of the second half of the project (i.e., the beginning of the spring semester).

\subsection{How can the contract be amended?}
\label{sec-9-3}
Changes to the contract will need to approval of the entire team. Proposed changes can be done by any team member.

\section{Affirmation of Compliance}
\label{sec-10}
We, the members of this team, Affirm that we have established this contract with input and consensus of all members. By our signatures, we commit to compliance with the contract for the benefit of all members and the team as a whole. 
\begin{center}
\begin{tabular}{lll}
\hline
\ \ \ \ Name & \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ Signature \ \ \ \ \ \ & \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ Date\\
\hline
Adams, Ranger & \hspace{50.0 mm} & \hspace{50.0 mm} \\
\hline
Bailey, Paul &  & \\
\hline
Brown, Matthew &  & \\
\hline
Huang, Heyan &  & \\
\hline
Thompson, Emeth &  & \\
\hline

\end{tabular}
\end{center}
% Emacs 24.3.1 (Org mode 8.2.7c)
\end{document}